\documentclass[11pt,letterpaper]{article}

\usepackage[letterpaper,margin=1in]{geometry}
\usepackage[utf8]{inputenc}
\usepackage{enumitem}
\usepackage{fancyhdr}
\usepackage{lastpage}
\usepackage{titlesec}
\usepackage{hyperref}
\usepackage{etaremune}

% Configure hyperlinks
\hypersetup{
    colorlinks=true,
    linkcolor=black,
    filecolor=black,
    urlcolor=blue,
    citecolor=black
}

% Page style
\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\cfoot{Page \thepage\ of \pageref{LastPage}}

% Section formatting
\titleformat{\section}{\large\bfseries\uppercase}{}{0em}{}[\titlerule]
\titleformat{\subsection}{\normalsize\bfseries}{}{0em}{}
\titlespacing{\section}{0pt}{12pt}{6pt}
\titlespacing{\subsection}{0pt}{8pt}{4pt}

% Custom commands
\newcommand{\name}[1]{\begin{center}\textbf{\Large #1}\end{center}}
\newcommand{\contact}[1]{\begin{center}#1\end{center}}
\newcommand{\entry}[4]{\textbf{#1} \hfill #2 \\ \textit{#3} \hfill #4}
\newcommand{\publication}[1]{\item #1}

\begin{document}

\name{Dr. Sarah M. Thompson}

\contact{
Department of Computer Science, University of Excellence \\
123 Academic Drive, Research City, ST 12345 \\
Phone: (555) 123-4567 | Email: s.thompson@university.edu \\
Website: \href{https://www.sarahthompson.edu}{www.sarahthompson.edu} | 
ORCID: \href{https://orcid.org/0000-0000-0000-0000}{0000-0000-0000-0000}
}

\section{Research Interests}
Machine Learning, Natural Language Processing, Computational Linguistics, Human-Computer Interaction, Educational Technology

\section{Education}

\entry{Ph.D. in Computer Science}{2018}
{Massachusetts Institute of Technology}{Cambridge, MA}
\begin{itemize}[noitemsep]
    \item Dissertation: "Deep Learning Approaches for Multilingual Natural Language Understanding"
    \item Advisor: Prof. John A. Smith
    \item Committee: Prof. Jane Doe, Prof. Robert Johnson, Prof. Maria Garcia
\end{itemize}

\entry{M.S. in Computer Science}{2014}
{Stanford University}{Stanford, CA}
\begin{itemize}[noitemsep]
    \item Thesis: "Semantic Analysis of Social Media Text for Sentiment Classification"
    \item Advisor: Prof. Lisa Chen
\end{itemize}

\entry{B.S. in Computer Science, \textit{summa cum laude}}{2012}
{University of California, Berkeley}{Berkeley, CA}
\begin{itemize}[noitemsep]
    \item Minor in Linguistics
    \item Phi Beta Kappa, Tau Beta Pi
\end{itemize}

\section{Academic Appointments}

\entry{Associate Professor}{2023--Present}
{Department of Computer Science, University of Excellence}{Research City, ST}

\entry{Assistant Professor}{2018--2023}
{Department of Computer Science, University of Excellence}{Research City, ST}

\entry{Postdoctoral Research Fellow}{2018--2019}
{MIT Computer Science and Artificial Intelligence Laboratory}{Cambridge, MA}

\section{Publications}

\subsection{Peer-Reviewed Journal Articles}

\begin{etaremune}[leftmargin=0.5in]
\publication{Thompson, S.M., Johnson, R., \& Lee, K. (2024). "Transformer-based Models for Cross-lingual Sentiment Analysis." \textit{Journal of Machine Learning Research}, 25(3), 1-28.}

\publication{Chen, L., Thompson, S.M., \& Williams, A. (2023). "Ethical Considerations in Large Language Model Development." \textit{AI \& Society}, 38(4), 1245-1262.}

\publication{Thompson, S.M., \& Garcia, M. (2023). "Multilingual BERT for Low-Resource Language Processing." \textit{Computational Linguistics}, 49(2), 387-412.}

\publication{Thompson, S.M., Smith, J.A., \& Brown, D. (2022). "Neural Machine Translation for Educational Content Adaptation." \textit{Computers \& Education}, 185, 104-118.}

\publication{Rodriguez, P., Thompson, S.M., \& Kim, H. (2022). "Bias Detection in Natural Language Processing Models." \textit{Nature Machine Intelligence}, 4(8), 623-635.}

\publication{Thompson, S.M., Davis, R., \& Wilson, T. (2021). "Deep Learning for Automated Essay Scoring: A Comprehensive Study." \textit{Educational Technology Research and Development}, 69(3), 1421-1445.}

\publication{Thompson, S.M., \& Anderson, K. (2020). "Context-Aware Language Models for Dialogue Systems." \textit{ACM Transactions on Interactive Intelligent Systems}, 10(4), 1-32.}

\publication{Thompson, S.M., Miller, J., \& Taylor, S. (2019). "Attention Mechanisms in Neural Language Models: A Survey." \textit{IEEE Transactions on Neural Networks and Learning Systems}, 30(11), 3456-3471.}
\end{etaremune}

\subsection{Peer-Reviewed Conference Papers}

\begin{etaremune}[leftmargin=0.5in]
\publication{Thompson, S.M., et al. (2024). "Large Language Models for Code Generation: Challenges and Opportunities." In \textit{Proceedings of the 38th AAAI Conference on Artificial Intelligence} (pp. 12345-12352). AAAI Press.}

\publication{Lee, M., Thompson, S.M., \& Zhang, Y. (2023). "Few-Shot Learning for Domain Adaptation in NLP." In \textit{Proceedings of the 61st Annual Meeting of the Association for Computational Linguistics} (pp. 8765-8776). ACL.}

\publication{Thompson, S.M., \& Kumar, A. (2023). "Explainable AI for Educational Applications." In \textit{Proceedings of the 2023 Conference on Empirical Methods in Natural Language Processing} (pp. 4321-4332). EMNLP.}

\publication{Thompson, S.M., White, R., \& Black, S. (2022). "Multilingual Pre-training for Cross-lingual Transfer Learning." In \textit{Proceedings of the 60th Annual Meeting of the Association for Computational Linguistics} (pp. 5678-5689). ACL.}

\publication{Green, P., Thompson, S.M., \& Blue, Q. (2021). "Adversarial Training for Robust NLP Models." In \textit{Advances in Neural Information Processing Systems 34} (pp. 9876-9887). NeurIPS.}
\end{etaremune}

\section{Grants and Funding}

\entry{NSF CAREER Award}{2021--2026}
{National Science Foundation}{\$500,000}
\begin{itemize}[noitemsep]
    \item "Developing Inclusive and Robust Natural Language Processing Systems"
    \item Role: Principal Investigator
\end{itemize}

\entry{Google Research Scholar Award}{2022--2024}
{Google Research}{\$60,000}
\begin{itemize}[noitemsep]
    \item "Bias Mitigation in Large Language Models"
    \item Role: Principal Investigator
\end{itemize}

\entry{Amazon Research Award}{2020--2022}
{Amazon Science}{\$80,000}
\begin{itemize}[noitemsep]
    \item "Conversational AI for Educational Applications"
    \item Role: Principal Investigator
\end{itemize}

\section{Teaching}

\subsection{Courses Taught}

\textbf{University of Excellence} (2018--Present)
\begin{itemize}[noitemsep]
    \item CS 4850: Natural Language Processing (Fall 2019, 2020, 2021, 2022, 2023)
    \item CS 6850: Advanced Topics in NLP (Spring 2020, 2021, 2022, 2023, 2024)
    \item CS 3200: Introduction to Machine Learning (Fall 2018, Spring 2019)
    \item CS 1100: Introduction to Computer Science (Spring 2019)
\end{itemize}

\subsection{Student Supervision}

\textbf{Ph.D. Students}
\begin{itemize}[noitemsep]
    \item Michael Chen (2020--Present): "Multilingual Language Models for Low-Resource Languages"
    \item Jennifer Rodriguez (2021--Present): "Ethical AI in Natural Language Processing"
    \item David Kim (2022--Present): "Conversational AI for Educational Support"
\end{itemize}

\textbf{M.S. Students Graduated}
\begin{itemize}[noitemsep]
    \item Sarah Johnson (2023): "Bias Detection in Pre-trained Language Models"
    \item Robert Wilson (2022): "Neural Machine Translation for Technical Documentation"
    \item Lisa Anderson (2021): "Sentiment Analysis for Social Media Monitoring"
\end{itemize}

\section{Service}

\subsection{Editorial Service}
\begin{itemize}[noitemsep]
    \item Associate Editor, \textit{Computational Linguistics} (2023--Present)
    \item Guest Editor, \textit{AI Magazine} Special Issue on "AI in Education" (2022)
    \item Editorial Board Member, \textit{Journal of Educational Technology Research} (2021--Present)
\end{itemize}

\subsection{Conference Service}
\begin{itemize}[noitemsep]
    \item Program Committee Chair, EMNLP 2024
    \item Area Chair, ACL 2023, 2024
    \item Program Committee Member: NeurIPS (2020--2023), ICML (2021--2024), AAAI (2019--2024)
    \item Reviewer: Nature Machine Intelligence, Science, JMLR, TACL
\end{itemize}

\subsection{Professional Service}
\begin{itemize}[noitemsep]
    \item Member, NSF CISE Advisory Committee (2023--2026)
    \item Chair, University Excellence Faculty Search Committee (2022--2023)
    \item Member, ACL Ethics Committee (2021--2024)
\end{itemize}

\section{Awards and Honors}

\begin{itemize}[noitemsep]
    \item Outstanding Faculty Award, University of Excellence (2023)
    \item NSF CAREER Award (2021)
    \item Best Paper Award, EMNLP 2023
    \item Google Research Scholar Award (2022)
    \item Rising Star in AI Award, AI2 (2020)
    \item Outstanding Teaching Award, University of Excellence (2019)
    \item Best Dissertation Award, MIT EECS (2018)
\end{itemize}

\section{Professional Memberships}

\begin{itemize}[noitemsep]
    \item Association for Computational Linguistics (ACL)
    \item Association for the Advancement of Artificial Intelligence (AAAI)
    \item Institute of Electrical and Electronics Engineers (IEEE)
    \item Association for Computing Machinery (ACM)
\end{itemize}

\section{Selected Invited Talks}

\begin{itemize}[noitemsep]
    \item "The Future of Multilingual AI," Keynote, International Conference on Computational Linguistics, 2024
    \item "Ethical Considerations in Large Language Models," Stanford AI Lab Seminar, 2023
    \item "Cross-lingual Transfer Learning," Google Research, 2023
    \item "NLP for Education," Microsoft Research, 2022
    \item "Bias in Language Models," MIT CSAIL Seminar, 2021
\end{itemize}

\end{document}
